From Principles to Practice with Class in the First Year

### 2013-04-12 tfpie/tfpie.tex
Progress.

\title{From Principles to Fashion with Class}
\author{Sam Tobin-Hochstadt \quad\qquad David Van Horn
\institute{Northeastern University\\
Boston, Massachusetts, USA}
\email{\{samth,dvanhorn\}@ccs.neu.edu}
}
\def\titlerunning{A Longtitled Paper}
\def\authorrunning{S. Tobin-Hochstadt \& D. Van Horn}
\begin{document}
\maketitle

@@

@@

@@

@@

\subsection{Representation-indepence and interface-oriented programming}

\section{From principles to fashions}

@@

\section{Comparison with HtDC}

@@

\cite{dvanhorn:Allen2002DrJava}

@@

@@

\begin{itemize}
\item changes languages from first semester rather than adding new
  concept (causes students confusing deep issue (O.O. design) and
  shallow ones (Java-like syntax) and orthogonal issues (static type
  discipline).  (This also ultimately lead to the tool being abandoned
  as it was too difficult to maintain.)

@@

>>>>

\title{From Principles to Practice with Class in the First Year}
\author{Sam Tobin-Hochstadt \quad\qquad David Van Horn
\institute{Northeastern University\\
Boston, Massachusetts, USA}
\email{\{samth,dvanhorn\}@ccs.neu.edu}
}
\def\titlerunning{A Longtitled Paper}
\def\authorrunning{S. Tobin-Hochstadt \& D. Van Horn}
\begin{document}
\maketitle

@@

\begin{itemize}
\item Lots of universities want their students to be proficient in an
  industrial object-oriented programming language by the end of the first year.
\item Teaching Java on Day 1 is a flawed approach.
\item Teaching functional programming in Semester 1 and Java in Semester 2 is a flawed approach.
\item We contribute a solution: a gradual transition from functional
  programming to object-oriented programming that culminates in
  industrial language proficiency.
\end{itemize}

@@

Context and contraints: HtDP vs. industrial co-op and subsequent Java courses.

Universe and world \cite{dvanhorn:Felleisen2009Functional}.

@@

\begin{enumerate}
\item Lists of numbers
\item World
\end{enumerate}

@@

\section{From principles to industrial languages}

@@

\subsection{Representation-independence and interface-oriented programming}

\section{Related work}

@@

\cite{dvanhorn:Allen2002DrJava, dvanhorn:Hsia2005Taming}

@@

\cite{dvanhorn:Bruce2001Library}

\cite{dvanhorn:Alphonce2003Using}

\cite{dvanhorn:Chakravarty2004Risks}

\cite{dvanhorn:Ragde2008Chilling}

\cite{dvanhorn:Bloch2000Scheme}

@@

\begin{itemize}
\item dead.
\item changes languages from first semester rather than adding new
  concept (causes students confusing deep issue (O.O. design) and
  shallow ones (Java-like syntax) and orthogonal issues (static type
  discipline).  (This also ultimately lead to the tool being abandoned
  as it was too difficult to maintain.)

@@

Other steps:
\begin{itemize}
\item types in class language
\item pedagogical Java environment
\item ugly syntax for class language
\item world in Java
\end{itemize}

\cite{dvanhorn:sicp}
